Too Much Automation? The Bellwether Effect and Its Implications for Transfer Learning

### 2016-12-02 doc/final/manuscript.tex
Makefile Commit

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

@@

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{ISSTA}{'17 Santa Barbara, CA USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Multi-Objective Search in Automated Patch Generation
\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as
%\textit{Author's Guide to Preparing ACM SIG Proceedings Using
%\LaTeX$2_\epsilon$\ and BibTeX} at
%\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor Rahul Krishna\\ %\titlenote{North Carolina State University}\\
       \affaddr{North Carolina State University}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       %\affaddr{Wallamaloo, New Zealand}\\
       \email{rkrish11@ncsu.edu}
% 2nd. author
\alignauthor Anwesha Das \\%\titlenote{North Carolina State University.}\\
       \affaddr{North Carolina State University}\\
       %\affaddr{P.O. Box 1212}\\
       %\affaddr{Dublin, Ohio 43017-6221}\\
       \email{adas4@ncsu.edu}
% 3rd. author
%\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
%one who did all the really hard work.}\\
 %      \affaddr{The Th{\o}rv{\"a}ld Group}\\
  %     \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
  %     \affaddr{Hekla, Iceland}\\
  %     \email{larst@affiliation.org}
%\and  % use '\and' if you need 'another row' of author names
% 4th. author
%\alignauthor Lawrence P. Leipuner\\
 %      \affaddr{Brookhaven Laboratories}\\
  %     \affaddr{Brookhaven National Lab}\\
   %    \affaddr{P.O. Box 5000}\\
    %   \email{lleipuner@researchlabs.org}
% 5th. author
%\alignauthor Sean Fogarty\\
 %      \affaddr{NASA Ames Research Center}\\
 %      \affaddr{Moffett Field}\\
 %      \affaddr{California 94035}\\
 %      \email{fogartys@amesres.org}
% 6th. author
%\alignauthor Charles Palmer\\
 %      \affaddr{Palmer Research Laboratories}\\
  %     \affaddr{8600 Datapoint Drive}\\
  %     \affaddr{San Antonio, Texas 78229}\\
  %     \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{2nd Dec 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
%\begin{CCSXML}
%<ccs2012>
 %<concept>
  %<concept_id>10010520.10010553.10010562</concept_id>
  %<concept_desc>Program Repair</concept_desc>
  %<concept_significance>500</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010575.10010755</concept_id>
  %<concept_desc>Genprog</concept_desc>
  %<concept_significance>300</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10010520.10010553.10010554</concept_id>
  %<concept_desc>Multi-objective</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
 %<concept>
  %<concept_id>10003033.10003083.10003095</concept_id>
  %<concept_desc>Fitness</concept_desc>
  %<concept_significance>100</concept_significance>
 %</concept>
%</ccs2012>  
%\end{CCSXML}

%\ccsdesc[500]{Program Repair}
%\ccsdesc[300]{Genprog}
%\ccsdesc{Multi-objective}
%\ccsdesc[100]{Fitness}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Program Repair; Genprog; Multi-objective}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{Background}

@@

\section{Discussion}

\section{Conclusion}

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{fly}
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{fly}
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic
that needs to span two columns of text.}
\end{figure*}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{rosette}
\caption{A sample black and white graphic that has
been resized with the \texttt{includegraphics} command.}
\vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{papers}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

>>>>

\documentclass[]{sig-alternate}
%\usepackage{stfloats}
\usepackage{tikz}
\def\firstcircle{(90:1.75cm) circle (2.5cm)}
\def\secondcircle{(210:1.75cm) circle (2.5cm)}
\def\thirdcircle{(330:1.75cm) circle (2.5cm)}

\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

% inner sep=10pt,
\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
fill=Gray!20,  drop shadow={fill=black, opacity=1}]
\newcommand\thmbox[1]{%
	\noindent\begin{tikzpicture}%
	\node [thmbox] (box){%
		\begin{minipage}{.94\textwidth}%
		\vspace{-3mm}#1\vspace{-3mm}%
		\end{minipage}%
	};%
	\end{tikzpicture}}

\let\theoremframecommand\thmbox
\newshadedtheorem{lesson}{Research answer}

\usepackage{booktabs}
\usepackage{comment}
\usepackage{cite}
\usepackage{framed,graphicx,xcolor}
\usepackage{multirow}
\usepackage{rotating}
%\usepackage{stfloats}
\usepackage[shortlabels]{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{balance}
\usepackage{bigstrut}
\newcommand{\bi}{\begin{itemize}}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
	\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sect:#1}}
\newcommand{\tab}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
%\setlist{nolistsep,leftmargin=5mm}
%\usepackage[pdftex]{graphicx}
% \usepackage{program}
\newcommand{\Sample}{{\bf SAMPLE}}
\newcommand{\PEEKING}{{\bf PEEKING2}}
%\usepackage[table]{xcolor}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
\definecolor{Blue}{RGB}{0,29,193}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{url}
\usepackage{hyphenat}
% \usepackage{hyperref}
%\usepackage{listings}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\definecolor{Code}{rgb}{0,0,0}
\definecolor{Decorators}{rgb}{0.5,0.5,0.5}
\definecolor{Numbers}{rgb}{0.5,0,0}
\definecolor{MatchingBrackets}{rgb}{0.25,0.5,0.5}
\definecolor{Keywords}{rgb}{0,0,1}
\definecolor{self}{rgb}{0,0,0}
\definecolor{Strings}{rgb}{0,0.63,0}
\definecolor{Comments}{rgb}{0,0.63,1}
\definecolor{Comments}{rgb}{0.5,0.5,0.5}
\definecolor{Backquotes}{rgb}{0,0,0}
\definecolor{Classname}{rgb}{0,0,0}
\definecolor{FunctionName}{rgb}{0,0,0}
\definecolor{Operators}{rgb}{0,0,0}
\definecolor{Background}{rgb}{1,1,1}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\newcommand{\G}{\cellcolor{green}}
\newcommand{\Y}{\cellcolor{yellow}}

\newcommand{\quart}[4]{\begin{picture}(80,4)%1
	{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}
\usepackage{url}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\newenvironment{changed}{\par\color{MyDarkBlue}}{\par}
%\newenvironment{changed}{\par}{\par}

\newcommand{\ADD}[1]{\textcolor{MyDarkBlue}{{\bf #1}}}
\usepackage{times}
% \pagenumbering{arabic}
\usepackage[splitrule]{footmisc} %% The splitrule option draws a full width
%%rule above the continued part of the footnote as a visual cue to readers.
\usepackage{balance}
% \usepackage{flushend}
\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

@@

     \definecolor{shadecolor}{gray}{0.9}
     \conferenceinfo{CSC791:}{Automated Program Repair}
     \title{Too Much Automation? The Bellwether Effect and Its Implications for Transfer Learning}
     \numberofauthors{1}
     \author{
     	\alignauthor
     	Rahul~Krishna \hspace{40pt} Anwesha~Das\\
     	\affaddr{Computer Science, North Carolina State University, USA}\\
     	{\{rkrish11, adas4\}@ncsu.edu}}
     \maketitle

		 \begin{abstract}

			 Automated Patch generation has garnered a lot of attention in the past decade. It has long been a elusive goal in software engineering. Automation has been a key research area and yet debugging/patch generation remains a largely manual process. One success story in this endeavor is \textit{GenProg} . In fact, GenProg, which is widely accepted as a promising tool by the research community, is now used as a baseline to compare other new techniques. Albeit popular, there is a general lack of consensus on the need for such complex tools to generate effective patches. While some researchers~\cite{leGoues12} opine that GenProg is quite effective in generating patches, given the existence of test cases, others \cite{qi2014, kim2013, arcuri2011} disagree. They say that it is quite unclear if the the efficacy of GenProg is merely due to its ``mutate'' operator or due to genetic programming.\\

			 \noindent{\bf Categories/Subject Descriptors:} D.2 [Software Engineering]; I.2
        [Artificial Intelligence];

		 \keywords{Defect Prediction; Data Mining; Transfer learning}
		 \end{abstract}

\section{Introduction}

This issue was examined by Qi et at.~\cite{qi2014}. With their tool RSRepair (\underline{\textit{R}}andom-\underline{\textit{S}}earch \underline{\textit{Repair}}), they demonstrated the benefit of random search over GenProg.

It is my hypothesis that the lack of efficiency of GenProg in this area is not due to the failure of Genetic Algorithms (or any evolutionary computation scheme for that matter), but due to incorrect and perhaps even incomplete modeling of the search space.

As a motivating example consider Genetic Programming. The algorithm works by trying to maximize the ``fitness'' score. In this case, the number of passing test cases given a patch. RSRepair, on the other hand, considers either repair effectiveness (as measured by the number patch trials required) or repair efficiency (measured by the number of test case executions). It not hard to see that each of these objectives namely, the number of passing test cases, the repair effectiveness, and the repair efficiency, are all important. Perhaps some are more important than others, but they all play a crucial role nonetheless.

Therefore, I conjecture that the research in the area of automated patch generation will be best guided by modeling the domain as a multiobjective search problem with the aforementioned objectives. This, in my opinion, will allow us to leverage the wealth of research in Search Based Software Engineering (referred to henceforth as \textit{SBSE}). To this end, this project asks the following two research questions:

\subsubsection*{RQ1: Can automated patch generation be modeled as a multiobjective search problem?}
Although it makes theoretical sense to view patch generation as containing multiple objectives, this question asks if it is practical to model it as such.

\subsubsection*{RQ2: If yes, what is the best multiobjective search to generate patches automatically?}
\label{rq2}
If the answer to RQ1 is affirmative. This question aims to explore various multiobjective optimizers to identify the best algorithm. Specifically, this project will compare three standard SBSE techniques: NSGAII, MOEAD, Genetic Programming, using Random Search as a baseline. In addition to this, the usefulness of a promising new algorithm called SWAY\footnote{This algorithm is in current development by our research group}~\cite{chen2016sampling, nair2016accidental} will be also be investigated.

\section{An Overview of Patch Generation}

Generally, when a bug is reported, an automated program repair scheme undertakes the following three steps:

\begin{enumerate}
    \item \textit{Fault localization:}
    These techniques are used to identify suspicious faulty code snippet that may a have caused the bug.

    \item \textit{Patch Generation:}
    Once faulty code snippet has been located, many candidate patches can be generated through the modifications to that code snippet, according to specific repair rules based on either evolutionary computation or code-based contracts.

    \item \textit{Patch Validation:}
    When a candidate patch has been produced, regression testing, inclusive of negative test cases (reproducing the fault) and positive test cases (characterizing the normal behaviors), is commonly used to validate the correctness of produced candidate patch.

\end{enumerate}

The above procedure can be iterated over and over again until some valid patch is found. Any patch passing all these test cases is considered valid.

\input{aux_tex/measures.tex}
\section{A (very) Brief Overview of Multiobjective Search}

A search is the task of finding one or more solutions which satisfy one or more specified objectives. While a single-objective optimization involves a single objective function and a single solutions, a multiobjective optimization considers several objectives simultaneously. In reference to the current problem we have three competing objectives, all of which need to be maximized: (1) Number of passing test cases; (2) The repair effectiveness; and (3) The repair efficiency

In such a case, a multiobjective optimizer generates a set of alternate solution with certain trade-offs. These are called \textit{Pareto Optimal Solutions}. The solutions, in our case, will be a set of valid patches that perform equally well when measured in terms of the three objectives.

Multiobjective problems are usually complex, NP-Hard, and resource intensive. Although exact methods can be used, they consume prohibitively large amounts of time and memory. An alternative approach would be to make use of metaheuristic algorithms from RQ2. These approximate the Pareto frontier in a reasonable amount of time.

@@

%\input{aux_tex/datasets.tex}

\subsection{Metrics}
Figure \ref{fig:measure} highlights some of the preliminary performance evaluation measures we use to evaluate the algorithms. Please note that this will be expanded in future to accommodate other measures.

\subsubsection{How to calculate them?}
Calculating these metrics are well studied~\cite{deb2002fast, goel2010study}. We have an implementation in place that can readily give these metrics, given a set of ideal solutions (in this case, valid patches).

\subsection{Datasets}
The data set required for evaluating will be obtained from some recent work on GenProg~\cite{leGoues12}. My reading of the literature suggests that these dataset are the ``benchmarks'', used by several researchers~\cite{qi2014}. These are C programs with all the bugs reported reported in the historical versions as tabulated in Figure~\ref{fig:datasets}.

\subsection{Tools}
As for tools, it is worth noting that AST can be generated from C programs using a tool called CIL\footnote{https://sourceforge.net/projects/cil/}.

\subsection{Analysis Plan}
To provide a more comprehensive comparison, the optimizers will be ranked ranked statistically. To do this, I shall use the Scott-Knott procedure recommended by Mittas \& Angelis\cite{mittas13}.

This method sorts a list of $l$ treatments with $ls$ measurements by their median
score. It then
splits $l$ into sub-lists $m,n$ in order to maximize the expected value of
differences  in the observed performances
before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$:
\[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
Scott-Knott then applies some statistical hypothesis test $H$ to check
if $m,n$ are significantly different. If so, Scott-Knott then recurses on each division.

\section{Proposed Timeline}

Figure \ref{time} highlights the proposed timeline for the tasks undertaken in the project. Please note again that this subject to change, please see https://github.com/ai-se/spatch/milestones for the latest milestone progress.\\
\pagebreak
\bibliographystyle{unsrt}
\bibliography{References}
\end{document}
